Concave reduction of swarm voids

### 2018-06-05 paper.tex
Structure Changes

Researchers have identified several approaches to resolving swarm structure issues. A prototype framework for self healing swarms was developed by Dai et al.~\cite{DHMRZ:06} which considered the problem of agent failure in hostile environments. This is in line with work carried out by Vassev and Hinchey~\cite{VH:09} who model swarm deployment using ASSL (Autonomic System Specification Language). This technique was used by NASA (National Aeronautics and Space Administration) when developing their ANTS (Autonomous Nano Technology Swarm) for use in asteroid belt exploration. This line of research is more focused towards an agent's internal systems failure rather than the removal of anomalies in a swarm distribution. Roach et al. \cite{RMT:15} take a different approach and focus on the effects of sensor failure and the effect that has on agent distribution. The closest research to concave reduction as discusssed in this paper is that of Lee and Chong \cite{GN:08} who identify the issue of concave edges within swarms in an attempt to create regular lattice formations. The main focus of their paper is the restructuring of the internal distribution of inter-agent formations. The research by Ismail and Timmis \cite{IT:10} used the approach of \textit{bio-inspired} healing using \textit{granuloma formation}, a biological method for encapsulating an antigen.

>>>>

Researchers have identified several approaches to resolving swarm structure issues. A prototype framework for self healing swarms was developed by Dai et al. which considered the problem of agent failure in hostile environments~\cite{DHMRZ:06}. This is in line with work carried out by Vassev and Hinchey who model swarm deployment using ASSL (Autonomic System Specification Language)~\cite{VH:09}. This technique was used by NASA (National Aeronautics and Space Administration) when developing their ANTS (Autonomous Nano Technology Swarm) for use in asteroid belt exploration. This line of research is more focused towards an agent's internal systems failure rather than the removal of anomalies in a swarm distribution. Roach et al. take a different approach and focus on the effects of sensor failure and the effect that has on agent distribution~\cite{RMT:15}. The closest research to concave reduction as discusssed in this paper is that of Lee and Chong who identify the issue of concave edges within swarms in an attempt to create regular lattice formations~\cite{GN:08}. The main focus of their paper is the restructuring of the internal distribution of inter-agent formations. The research by Ismail and Timmis used the approach of \textit{bio-inspired} healing using \textit{granuloma formation}, a biological method for encapsulating an antigen~\cite{IT:10}.
